Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-10 R0V0.tex
Minor typo
Item 22. See new paragraph# III.2

\mypara For large scale systems, the dimension of the matrices $W$ and $Y$ can be a problem for the computation of a solution to the MI~\eqref{eq:MI formulation}. This is due to the fact that semidefinite programming become less efficient when those matrices have high rank \cite{VandenbergheBoyd1996}. For this reason, the computation of a solution to MI~\eqref{eq:MI formulation} need to be done parallel. To this end some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.

>>>>

\mypara For large scale systems, the dimension of the matrices $W$ and $Y$ can be a problem for the computation of a solution to the MI~\eqref{eq:MI formulation}. This is due to the fact that semidefinite programming become less efficient when those matrices have high rank \cite{VandenbergheBoyd1996}. For this reason, the computation of a solution to MI~\eqref{eq:MI formulation} need to be done in parallel.

\mypara To that end three methodologies are recalled below: chordal graphs, alternating direction of multipliers (ADMM) and scaled diagonal dominance. The first exploits the network topology to decompose it into smaller connected components. The second method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality below. Finally, scaled diagonal dominance exploits the stability of individual agents (i.e., when these considered not connected to the network) and weak coupling. Note that these methodologies can be used either separately or together. The latter would appropriate, when the smaller components of the network have high rank. Some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}.
